### 2024-05-27 getting-started.qmd
20240526 - placeholder
20240526 - load ffanalytics package

```{r}
library("nflreadr")
library("nflfastR")
library("nfl4th")
library("nflplotR")
library("progressr")
library("lubridate")
library("tidyverse")
```

@@

>>>>

```{r}
library("ffanalytics")
library("nflreadr")
library("nflfastR")
library("nfl4th")
library("nflplotR")
library("progressr")
library("lubridate")
library("tidyverse")
```

@@

#### Weekly {#sec-calculateActualPointsWeekly}

#### Seasonal {#sec-calculateActualPointsWeekly}

#### Career {#sec-calculateActualPointsWeekly}
